---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r eval=FALSE, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rtichoke

<!-- badges: start -->
[![R-CMD-check](https://github.com/uriahf/rtichoke/workflows/R-CMD-check/badge.svg)](https://github.com/uriahf/rtichoke/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/rtichoke)](https://CRAN.R-project.org/package=rtichoke)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/uriahf/rtichoke/branch/main/graph/badge.svg)](https://codecov.io/gh/uriahf/rtichoke?branch=main)
<!-- badges: end -->

## Installation 

<!-- You can install the released version of rtichoke from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("rtichoke") -->
<!-- ``` -->

You can install rtichoke from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("uriahf/rtichoke")
```

## Overview: 

rtichoke is a package designed for interactive visualization for performance metrics of prediction models with a binary outcome.

## Getting started

### Predictions and Outcomes

In order to use rtichoke you need to have 

1. `probs`: Estimated Probabilities as predictions ($0 \leq\hat{p} \leq 1$).
2. `real`: Binary Outcomes ($y∈\{1, 0\}$). 

There are 3 different cases and for each one of them rtichoke requires a different kind of input:

1. One model for One Population: 

The user is required to provide one vector for the model's predictions and one 
vector for the outcome of the population.

For example a Logistic Regression 🔀:

! 
We will use median imputation for the age variable, it is not a good practice 
for imputation but it is easy to understand and it allows us to use the `Age` 
variable.

```{r eval=FALSE, include=FALSE}

library(rtichoke)
library(titanic)

data("titanic_train")

titanic_train$Age[is.na(titanic_train$Age)] <- median(titanic_train$Age, 
                                                      na.rm = TRUE)

logistic_regression <- glm(Survived ~ Age + Sex, family = "binomial", data = titanic_train)

logistic_preds_train <- predict(logistic_regression, type = "response")
survived_train <- titanic_train$Survived

```
(gif)

```{r eval=FALSE, include=FALSE}

create_roc_curve(probs = logistic_preds_train,
                 real = survived_train,
                 interactive = TRUE)
```

<!-- TODO: Force cur ve to be squared  -->



Alternatively the vector of the model predictions can be in a list:

```{r eval=FALSE, include=FALSE}
create_roc_curve(probs = list("Logistic Regression" = 
                   logistic_preds_train),
                 real = survived_train,
                 interactive = TRUE)
```


2. Several models for One Population 🔀   

Let's say we want to compare performance for three different models:

The user is required to provide one vector of predictions for each model in a list and one vector for the outcome of the population.

This time we will use Decision Tree Model 🌲

```{r eval=FALSE, include=FALSE}
library(rpart)

fit <- rpart( Survived~ Age + Sex, data = titanic_train, method = 'class')

tree_model <- rpart(Survived ~ Age + Sex, data = titanic_train)

tree_preds_train <- predict(tree_model)

```

And just for fun we will add A random guess 🙈

```{r eval=FALSE, include=FALSE}

set.seed(123)

random_preds_train <- runif(nrow(titanic_train), 0, 1)

```


```{r eval=FALSE, include=FALSE}

create_roc_curve(probs = list(
  "Logistic Regression" = logistic_preds_train,
  "Decision Tree" = tree_preds_train,
  "Random Guess" = random_preds_train),
                 real = survived_train,
                 interactive = TRUE)

```


3. Several Populations 👩👨

The user is required to provide one vector of predictions for each population in a list and one vector for each outcome of the population in another list.

(code)
probs = list("Train" = …, "Test" = …), real = list("Train" = …, "Test" = …)
(gif)



### Performance Data

For roc, lift, precision recall, gains and decision curves and for performance table you can alternatively prepare a performance data and use it as an input, but instead of create_*_curve use plot_*_curve and instead of create_performance_table use render_performance_table:
(gif render_roc_curve, prepare_performance_table, plot_roc_curve)
(table of inputs)


### Summary Report 

In order to get all the supported outputs of rtichoke in one html file the user can call create_summary_report().

### Getting help

If you encounter a bug please fill an issue with a minimal reproducible example, it will be easier for me to help you and it might help others in the future. Alternatively you are welcome to contact me personally: ufinkel@gmail.com

