---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r eval=FALSE, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rtichoke

<!-- badges: start -->
[![R-CMD-check](https://github.com/uriahf/rtichoke/workflows/R-CMD-check/badge.svg)](https://github.com/uriahf/rtichoke/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/rtichoke)](https://CRAN.R-project.org/package=rtichoke)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/uriahf/rtichoke/branch/main/graph/badge.svg)](https://codecov.io/gh/uriahf/rtichoke?branch=main)
<!-- badges: end -->

## Installation 

<!-- You can install the released version of rtichoke from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("rtichoke") -->
<!-- ``` -->

You can install rtichoke from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("uriahf/rtichoke")
```
<!-- TODO change to good model, bad model and random guess -->
## Overview: 

rtichoke is a package designed for interactive visualization for performance metrics of prediction models with a binary outcome.

## Getting started

### Naming Convention

```{r echo=FALSE}

library(magrittr)

tibble::tribble(~"Output", ~"Predictions and Outcomes", ~"Performance Data",

                "Performance Data", "`prepare_performance_data()`", "",

                "ROC", "`create_roc_curve()`", "`plot_roc_curve()`",

                "Lift", "`create_lift_curve()`", "`plot_lift_curve()`",

                "Gains", "`create_gains_curve()`", "`plot_gains_curve()`",

                "Precision Recall", "`create_precision_recall_curve()`", "`plot_precision_recall_curve()`",

                "Decision", "`create_decision_curve()`", "`plot_decision_curve()`",

                "Calibration", "`create_calibration_curve()`", "",

                "Performance Table", "`create_performance_table()`", "`render_performance_table()`",

                "Summary Report", "`create_summary_report()`", "") %>%

  gt::gt(rowname_col = "Output")   %>%

  gt::fmt_markdown(columns = c("Predictions and Outcomes", "Performance Data"))  %>% 
  gt::tab_style(
    style = list(
      gt::cell_text(weight = "bold")
    ),
    locations = gt::cells_column_labels(dplyr::everything())
  )  %>% 
  gt::opt_table_lines(extent = "default") %>%
  gt::tab_options(
    column_labels.border.top.color = "white",
    column_labels.border.top.width = gt::px(3),
    column_labels.border.bottom.color = "black",
    table_body.hlines.color = "white",
    table.border.bottom.color = "white",
    table.border.bottom.width = gt::px(3)
  )

```

### Curves based on Performance Metrics

```{r echo=FALSE}
tibble::tribble(~"Curve", ~"Sens", ~"Spec", ~"PPV", ~"PPCR", ~"Lift", ~"NB", ~"P. Thr",
                "ROC","y", "x", " ", " ", " ", " ", " ",
                "Lift"," ", " ", " ", "x", "y", " ", " ",
                "Gains"," ", "y", " ", "x", " ", " ", " ",
                "Precision Recall","x", " ", "y", " ", " ", " ", " ",
                "Decision","x", " ", "y", " ", " ", "y", "x") %>%
  gt::gt(rowname_col = "Curve")   %>%
  gt::tab_style(
    style = list(
      gt::cell_text(weight = "bold")
    ),
    locations = gt::cells_column_labels(dplyr::everything())
  )  %>%
  gt::opt_table_lines(extent = "default") %>%
  gt::tab_options(
    column_labels.border.top.color = "white",
    column_labels.border.top.width = gt::px(3),
    column_labels.border.bottom.color = "black",
    table_body.hlines.color = "white",
    table.border.bottom.color = "white",
    table.border.bottom.width = gt::px(3)
  ) %>%
  gt::cols_align(
    align = "center"
  )


```


### Predictions and Outcomes as input

In order to use rtichoke you need to have 

- `probs`: Estimated Probabilities as predictions ($0 \leq\hat{p} \leq 1$).
- `real`: Binary Outcomes ($y∈\{1, 0\}$). 

There are 3 different cases and for each one of them rtichoke requires a different kind of input:

### One model for One Population: 

**Why?** 
In order to examine performance of a single model for one population.

**How?**
The user is required to provide one vector for the model's predictions and one vector for the outcome of the population.

```{r echo=FALSE}

library(rtichoke)
set.seed(123)

predictions_and_outcomes <- tibble::tibble(
  probs = example_dat$bad_model,
  real = as.numeric(
    rtichoke::example_dat$outcome)
  ) 


predictions_and_outcomes %>% 
  dplyr::sample_n(replace = FALSE, size = 6) %>% 
  gt::gt() %>% 
  gt::cols_align(align = "center") %>% 
  gt::fmt_number(columns = probs,
                 decimals  = 2)
```


```{r eval=FALSE, include=TRUE}

create_roc_curve(probs = example_dat$bad_model,
                 real = example_dat$outcome,
                 interactive = TRUE)
```

Alternatively the vector of the model predictions can be in a list:

```{r eval=FALSE, include=TRUE}
create_roc_curve(probs = list("Bad Model" = example_dat$bad_model),
                 real = example_dat$outcome,
                 interactive = TRUE)
```


### Several Models for One Population 

**Why?** 
In order to compare performance for several different models for the same population.

**How?** 
The user is required to provide one vector of predictions for each model in a list and one vector for the outcome of the population.


```{r echo=FALSE}

library(rtichoke)
set.seed(42)

predictions_and_outcomes <- tibble::tibble(
    "Good Model" = example_dat$estimated_probabilities,
    "Bad Model" = example_dat$bad_model,
    "Random Guess" = example_dat$random_guess,
  real = as.numeric(rtichoke::example_dat$outcome)) 


predictions_and_outcomes %>% 
  dplyr::sample_n(replace = FALSE, size = 6) %>% 
  gt::gt() %>% 
  gt::cols_align(align = "center") %>% 
  gt::fmt_number(columns = 1:3,
                 decimals  = 2)
```


```{r eval=FALSE, include = TRUE}
create_roc_curve(
  probs = list(
    "Good Model" = example_dat$estimated_probabilities,
    "Bad Model" = example_dat$bad_model,
    "Random Guess" = example_dat$random_guess
  ),
  real = as.numeric(rtichoke::example_dat$outcome),
  interactive = TRUE
)

```


### Several Populations 

*Why?* 
In order to compare performance for different populations, like in Train / Test
split or in order to check the fairness of the algorithms.

*How?* 
The user is required to provide one vector of predictions for each population in a list and one vector for each outcome of the population in another list.


```{r echo=FALSE}

library(rtichoke)
set.seed(42)

predictions_and_outcomes_train <- tibble::tibble(
    "probs" = example_dat %>%
      dplyr::filter(type_of_set == "train") %>%
      dplyr::pull(estimated_probabilities),
  real = example_dat %>% dplyr::filter(type_of_set == "train") %>%
      dplyr::pull(outcome) %>% 
    as.numeric())  

predictions_and_outcomes_test <- tibble::tibble(
    "probs" = example_dat %>%
      dplyr::filter(type_of_set == "test") %>%
      dplyr::pull(estimated_probabilities),
  real = example_dat %>% dplyr::filter(type_of_set == "test") %>%
      dplyr::pull(outcome) %>% 
    as.numeric())  



predictions_and_outcomes_train %>% 
  dplyr::sample_n(replace = FALSE, size = 6) %>% 
  gt::gt() %>%
  gt::tab_header(
    title = gt::md("**Train Set**")
  )  %>% 
  gt::fmt_number(columns = probs,
                 decimals  = 2)


predictions_and_outcomes_test %>% 
  dplyr::sample_n(replace = FALSE, size = 6) %>% 
  gt::gt() %>%
  gt::tab_header(
    title = gt::md("**Test Set**")
  )%>% 
  gt::fmt_number(columns = probs,
                 decimals  = 2)

```


```{r eval=FALSE, include = TRUE}

create_roc_curve(
  probs = list(
    "Train" = example_dat %>%
      dplyr::filter(type_of_set == "train") %>%
      dplyr::pull(estimated_probabilities),
    "Test" = example_dat %>% dplyr::filter(type_of_set == "test") %>%
      dplyr::pull(estimated_probabilities)
  ),
  real = list(
    "Train" = example_dat %>% dplyr::filter(type_of_set == "train") %>%
      dplyr::pull(outcome),
    "Test" = example_dat %>% dplyr::filter(type_of_set == "test") %>%
      dplyr::pull(outcome)
  ),
  interactive = TRUE
)

```



## Performance Data as input

For some outputs in rtichoke you can alternatively prepare a performance data and use it as an input:
instead of `create_*_curve` use `plot_*_curve` and instead of `create_performance_table` use `render_performance_table`:

```{r eval=FALSE, include = TRUE}
one_pop_one_model_as_a_vector %>%
  plot_roc_curve(interactive = TRUE)
```



### Summary Report 

In order to get all the supported outputs of rtichoke in one html file the user can call `create_summary_report()`.

### Getting help

If you encounter a bug please fill an issue with a minimal reproducible example, it will be easier for me to help you and it might help others in the future. Alternatively you are welcome to contact me personally: ufinkel@gmail.com



