---
title: "Calibration Analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Calibration Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Calibration evaluates agreement between predicted probabilities and observed event frequencies. A well-calibrated model predicting a $20\%$ risk of an outcome should observe approximately $20$ events per $100$ individuals with that prediction.

For detailed methodological background on calibration slope, intercept, and smooth recalibration, visit the [rtichoke blog](https://rtichoke-blog.netlify.app/).

---

## Creating Calibration Curves

In `rtichoke`, calibration curves display predicted probabilities on the x-axis against observed event proportions on the y-axis.

```{r eval=FALSE}
library(rtichoke)

create_calibration_curve(
  probs = list(
    "Good Model" = example_dat$estimated_probabilities,
    "Bad Model"  = example_dat$bad_model
  ),
  reals = list(example_dat$outcome)
)
```

### Reference Line

The 45-degree diagonal line ($y = x$) represents perfect calibration. Points above the line indicate underestimation of risk; points below indicate overestimation.

---

## Calibration Curve Options

`rtichoke` supports both binned (deciles) and smooth non-parametric (lowess) representations for calibration analysis:

- **Deciles (Binned):** Divides predictions into equal-sized subgroups and plots observed proportion vs. mean prediction in each bin.
- **Smooth (Lowess):** Fits a non-parametric smoother across the full range of predicted probabilities.

---

## Multiple Calibration Curves List

When analyzing multiple models or subgroups in list format:

```{r eval=FALSE}
create_calibration_curve_list(
  probs = list(
    "Good Model" = example_dat$estimated_probabilities,
    "Bad Model"  = example_dat$bad_model
  ),
  reals = list(example_dat$outcome)
)
```

---

## Capability Boundary & Scope Note

`rtichoke` in R currently provides calibration curves for binary prediction models evaluated on static outcomes.

*Note:* Time-dependent calibration across multiple follow-up time horizons is not implemented in `rtichoke` R. For binary classification outcomes, `create_calibration_curve()` is the canonical, authoritative implementation.
