---
title: "performance_data_examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{performance_data_examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rtichoke)
```

It is useful to work with Performance Datas for most functions in {rtichoke}.

There are several different cases for different Performance Datas:

## 1. One model for one population

When the user just want to observe the performance of one model. 

One can use a single vector as an input for the `probs` argument:

```{r}

one_pop_one_model_as_a_vector <- prepare_performance_data(
  probs = example_dat$estimated_probabilities,
  real = example_dat$outcome)

head(one_pop_one_model_as_a_vector)

one_pop_one_model_as_a_vector_enforced_percentiles_symmetry <- prepare_performance_data(
  probs = example_dat$estimated_probabilities,
  real = example_dat$outcome,
  enforce_percentiles_symmetry = T)

head(one_pop_one_model_as_a_vector_enforced_percentiles_symmetry)

```

```{r eval=FALSE, include=FALSE}
usethis::use_data(one_pop_one_model_as_a_vector, one_pop_one_model_as_a_vector_enforced_percentiles_symmetry)
```


Or alternatively a list with a single vector. In that case a column named "model" will be added to the Performance Data, it is recommended to name the vectors:

```{r}

one_pop_one_model_as_a_list <- prepare_performance_data(
  probs = list("Logistic Regression" = example_dat$estimated_probabilities),
  real = example_dat$outcome)

head(one_pop_one_model_as_a_list)

one_pop_one_model_as_a_list_enforced_percentiles_symmetry <- prepare_performance_data(
  probs = list("Logistic Regression" = example_dat$estimated_probabilities),
  real = example_dat$outcome,
  enforce_percentiles_symmetry = T)

head(one_pop_one_model_as_a_list_enforced_percentiles_symmetry)

```


```{r eval=FALSE, include=FALSE}
usethis::use_data(one_pop_one_model_as_a_list, one_pop_one_model_as_a_list_enforced_percentiles_symmetry)
```

## 2. Several models for one population

When the user wants to compare several models. 

One needs to use a list with a vector for each population as an input for the `probs` argument. it is recommended to name the vectors:

```{r}

one_pop_three_models <- prepare_performance_data(
  probs = list("Good Model" = example_dat$estimated_probabilities,
               "Bad Model" = example_dat$bad_model,
               "Random Guess" = example_dat$random_guess),
  real = example_dat$outcome)

one_pop_three_models_enforced_percentiles_symmetry <- prepare_performance_data(
  probs = list("Good Model" = example_dat$estimated_probabilities,
               "Bad Model" = example_dat$bad_model,
               "Random Guess" = example_dat$random_guess),
  real = example_dat$outcome, 
  enforce_percentiles_symmetry = T)

```


```{r eval=FALSE, include=FALSE}
usethis::use_data(one_pop_three_models, one_pop_three_models_enforced_percentiles_symmetry)
```


## 3. Several Populations 

When the user wants to compare model performance on different populations. 
Might be usefull when the user wants to check the consistensy of the model among different populations, a test-train split or fairness analysis might be good use cases.

One needs to use a list with a vector for each model as an input for the `probs` argument and for the `real` argument. A column named "population" will be added to the Performance Data, it is recommended to name the vectors:

```{r}

train_and_test_sets <- prepare_performance_data(
  probs = list("train" = example_dat %>%
                 dplyr::filter(type_of_set == "train") %>%
                 dplyr::pull(estimated_probabilities),
               "test" = example_dat %>% dplyr::filter(type_of_set == "test") %>%
                 dplyr::pull(estimated_probabilities)),
  real = list("train" = example_dat %>% 
                dplyr::filter(type_of_set == "train") %>%
                dplyr::pull(outcome),
              "test" = example_dat %>% 
                dplyr::filter(type_of_set == "test") %>%
                dplyr::pull(outcome)))

head(train_and_test_sets)

train_and_test_sets_enforced_percentiles_symmetry <- prepare_performance_data(
  probs = list("train" = example_dat %>%
                 dplyr::filter(type_of_set == "train") %>%
                 dplyr::pull(estimated_probabilities),
               "test" = example_dat %>% dplyr::filter(type_of_set == "test") %>%
                 dplyr::pull(estimated_probabilities)),
  real = list("train" = example_dat %>% 
                dplyr::filter(type_of_set == "train") %>%
                dplyr::pull(outcome),
              "test" = example_dat %>% 
                dplyr::filter(type_of_set == "test") %>%
                dplyr::pull(outcome)))

head(train_and_test_sets_enforced_percentiles_symmetry)


```


```{r eval=FALSE, include=FALSE}
usethis::use_data(train_and_test_sets, train_and_test_sets_enforced_percentiles_symmetry)
```
