---
title: "Performance Tables & Summary Reports"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Performance Tables & Summary Reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In addition to interactive curves, `rtichoke` generates structured, interactive performance tables and comprehensive HTML summary reports.

---

## Interactive Performance Tables

`rtichoke` performance tables summarize threshold-specific confusion matrix metrics (Sensitivity, Specificity, PPV, NPV, FPR, FNR, Accuracy, Net Benefit) across probability cutoffs.

### One-Step Table Creation (`create_performance_table`)

```{r eval=FALSE}
library(rtichoke)

create_performance_table(
  probs = list(
    "Good Model" = example_dat$estimated_probabilities,
    "Bad Model"  = example_dat$bad_model
  ),
  reals = list(example_dat$outcome)
)
```

### Rendering Table from Prepared Data (`render_performance_table`)

When performance data has already been prepared with `prepare_performance_data()`, use `render_performance_table()`:

```{r eval=FALSE}
perf_data <- prepare_performance_data(
  probs = list(
    "Good Model" = example_dat$estimated_probabilities,
    "Bad Model"  = example_dat$bad_model
  ),
  reals = list(example_dat$outcome)
)

render_performance_table(perf_data)
```

---

## Comprehensive HTML Summary Reports

`create_summary_report()` bundles all `rtichoke` interactive visualizations (ROC, Precision-Recall, Gains, Lift, Decision Curve, Calibration Curve, and Performance Tables) into a single, self-contained HTML file.

```{r eval=FALSE}
create_summary_report(
  probs = list("Primary Model" = example_dat$estimated_probabilities),
  reals = list(example_dat$outcome),
  file_path = "model_performance_report.html"
)
```

This report is ideal for sharing comprehensive model evaluation results with collaborators, clinical stakeholders, or model validation review boards.
