---
title: "Recipes & Canonical Workflows"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Recipes & Canonical Workflows}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This page serves as a compact, authoritative recipe guide for data scientists and automated coding agents using `rtichoke` in R.

---

## 1. Single Binary Classification Model

Evaluate predictions from one model on a single dataset.

```{r eval=FALSE}
library(rtichoke)

# Input vectors
probs_vector <- example_dat$estimated_probabilities
reals_vector <- example_dat$outcome

# ROC Curve
create_roc_curve(
  probs = list(probs_vector),
  reals = list(reals_vector)
)

# Precision-Recall Curve
create_precision_recall_curve(
  probs = list(probs_vector),
  reals = list(reals_vector)
)

# Decision Curve
create_decision_curve(
  probs = list(probs_vector),
  reals = list(reals_vector)
)

# Calibration Curve
create_calibration_curve(
  probs = list(probs_vector),
  reals = list(reals_vector)
)
```

---

## 2. Comparing Multiple Models on the Same Population

Compare multiple models evaluated on identical subjects and outcomes using a named list.

```{r eval=FALSE}
# Named list of predictions, single outcome vector in list
create_roc_curve(
  probs = list(
    "Model A (Good)" = example_dat$estimated_probabilities,
    "Model B (Bad)"  = example_dat$bad_model,
    "Model C (Random)" = example_dat$random_guess
  ),
  reals = list(example_dat$outcome)
)
```

---

## 3. Evaluating Across Distinct Subgroups or Split Sets

Compare one model across distinct cohorts (e.g., Train vs. Test split or demographic groups).

```{r eval=FALSE}
train_df <- example_dat[example_dat$type_of_set == "train", ]
test_df  <- example_dat[example_dat$type_of_set == "test", ]

create_roc_curve(
  probs = list(
    "Train Cohort" = train_df$estimated_probabilities,
    "Test Cohort"  = test_df$estimated_probabilities
  ),
  reals = list(
    "Train Cohort" = train_df$outcome,
    "Test Cohort"  = test_df$outcome
  )
)
```

---

## 4. Reusable Prepared Data Pipeline

Prepare metrics once and generate multiple visualizations efficiently.

```{r eval=FALSE}
perf_data <- prepare_performance_data(
  probs = list(
    "Model A" = example_dat$estimated_probabilities,
    "Model B" = example_dat$bad_model
  ),
  reals = list(example_dat$outcome)
)

# Reuse prepared object across all evaluation functions
plot_roc_curve(perf_data)
plot_precision_recall_curve(perf_data)
plot_gains_curve(perf_data)
plot_lift_curve(perf_data)
plot_decision_curve(perf_data)
render_performance_table(perf_data)
```

---

## 5. Automated HTML Summary Report

Generate a single interactive HTML file containing all evaluations and performance tables.

```{r eval=FALSE}
create_summary_report(
  probs = list("Primary Model" = example_dat$estimated_probabilities),
  reals = list(example_dat$outcome),
  file_path = "model_evaluation_report.html"
)
```

---

## 6. Supported Capabilities & Boundaries Summary

| Feature / Output | Supported in `rtichoke` R | Input Format |
| :--- | :---: | :--- |
| **ROC Curve** | Yes | `probs = list(...)`, `reals = list(...)` |
| **Precision-Recall Curve** | Yes | `probs = list(...)`, `reals = list(...)` |
| **Gains Curve** | Yes | `probs = list(...)`, `reals = list(...)` |
| **Lift Curve** | Yes | `probs = list(...)`, `reals = list(...)` |
| **Decision Curve (Net Benefit)** | Yes | `probs = list(...)`, `reals = list(...)` |
| **Interventions Avoided** | Yes | Integrated in Decision Curve outputs |
| **Calibration Curve** | Yes | Deciles / Smooth options available |
| **Performance Tables** | Yes | Threshold-specific metrics summary |
| **HTML Summary Report** | Yes | `create_summary_report()` |
| **Time-Dependent Horizons (`_times`)** | No | Not implemented in R package |
| **Time-Dependent Calibration** | No | Not implemented in R package |
