---
title: "Summary Report"
output: 
  html_document:
    toc: true
params:
  probs: NA
  reals: NA
  interactive: NA
---

```{=html}
<style type="text/css">
.main-container {
  max-width: 1040px;
  margin-left: auto;
  margin-right: auto;
}
</style>
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(rtichoke)
library(dplyr)
```

<details>

<summary>

Performance Metrics Cheat Sheet

</summary>

<br>

```{r}
tibble::tribble(
  ~"type", ~"predicted_positive", ~"predicted_negative",
  "Real Positive", "TP", "FN",
  "Real Negative", "FP", "TN"
) %>% 
  reactable::reactable(sortable = FALSE,
            fullWidth = FALSE,
            borderless = FALSE,
            defaultColDef = reactable::colDef(
              align = "center",
              headerStyle  = list(fontWeight = 100)
            ),
            columns = list(
              type = reactable::colDef(
                name = "",
                align = "left",
                style = list(fontWeight = 100),
                minWidth = 110
              ),
              predicted_positive = reactable::colDef(
                name = "Predicted Positive",
                style = function(value) {
                  color <- if (value == "TP") {
                    "lightgreen"
                  } else if (value == "FP") {
                    "pink"
                  }
                  list(fontWeight = 600, background = color)
                }
            ),
            predicted_negative = reactable::colDef(
              name = "Predicted Negative",
              style = function(value) {
                color <- if (value == "TN") {
                  "lightgreen"
                } else if (value == "FN") {
                  "pink"
                }
                list(fontWeight = 600, background = color)
              }
            )
            )
  )
```

<br> <br> $\begin{aligned} {\text{Prevalence}} = \frac{\text{TP + FN}}{\text{TP + FP + TN + FN}} \end{aligned}$

<br>

$\begin{aligned} {\text{PPCR (Predicted Positives Condition Rate)}} = \frac{\text{TP + FP}}{\text{TP + FP + TN + FN}} \end{aligned}$

<br>

$\begin{aligned} \text{Sensitivity (Recall, True Positive Rate)} = \frac{\text{TP}}{\text{TP + FN}} = \frac{\text{TP}}{\text{Real Positives}} = \text{Prob( Predicted Positive | Real Positive )} \end{aligned}$

<br>

$\begin{aligned} \text{Specificity (True Negative Rate)} = \frac{\text{TN}}{\text{TN + FP}} = \frac{\text{TN}}{\text{Real Negatives}} = \text{Prob( Predicted Negative | Real Negative )} \end{aligned}$

<br>

$\begin{aligned}  \text{PPV (Precision)} = \frac{\text{TP}}{\text{TP + FP}} = \frac{\text{TP}}{\text{Predicted Positives}} = \text{Prob( Real Positive | Predicted Positive )} \end{aligned}$

<br>

$\begin{aligned}  \text{NPV} = \frac{\text{TN}}{\text{TN + FN}} = \frac{\text{TN}}{\text{Predicted Negatives}} = \text{Prob( Real Negative | Predicted Negative )} \end{aligned}$

<br>

$\begin{aligned} \text{Lift} = \frac{\text{PPV}}{\text{Prevalence}} = \frac{\cfrac{\text{TP}}{\text{TP + FP}}}{\cfrac{\text{TP + FN}}{\text{TP + FP + TN + FN}}} \end{aligned}$

<br>

$\begin{aligned} \text{Net Benefit} = \frac{\text{TP}}{\text{TP + FP + TN + FN}} - \frac{\text{FP}}{\text{TP + FP + TN + FN}} * {\frac{{p_{t}}}{{1 - p_{t}}}} \end{aligned}$

<br>

</details>

<br> <br>

```{r message=FALSE, warning=FALSE}
performance_dat <- prepare_performance_data(probs = params$probs, 
                         reals = params$reals)
```

```{r}
create_table_for_prevalence(performance_dat)
```

# Calibration {.tabset}

## Smooth

```{r message=FALSE, warning=FALSE}
create_calibration_curve(probs = params$probs, 
                         reals = params$reals, 
                         interactive = params$interactive, 
                         type = "smooth", size = 550) 
```

## Discrete

```{r message=FALSE, warning=FALSE}
create_calibration_curve(probs = params$probs, 
                         reals = params$reals, 
                         interactive = params$interactive, 
                         size = 550) 
```

# Discrimination {.tabset}

```{r}
create_table_for_auc(probs = params$probs, 
                     reals = params$reals)
```

## By Probability Threshold

### Performance Metrics Curves {.tabset}

#### ROC

```{r}
plot_roc_curve(performance_dat, interactive = params$interactive, 
               size = 500) 
  
```

#### Lift

```{r}
plot_lift_curve(performance_dat, interactive = params$interactive, 
                size = 500) 
```

#### Precision Recall

```{r}
plot_precision_recall_curve(performance_dat, interactive = params$interactive,
                            size = 500) 
```

#### Gains

```{r}
plot_gains_curve(performance_dat, interactive = params$interactive, 
                 size = 500) 
```

## By Predicted Positives Condition Rate (PPCR)

### Performance Metrics Curves {.tabset}

#### ROC

```{r message=FALSE, warning=FALSE}
performance_dat_ppcr <- prepare_performance_data(probs = params$probs, 
                         reals = params$reals, 
                         stratified_by = "ppcr")
```

```{r}
plot_roc_curve(performance_dat_ppcr, interactive = params$interactive,
               size = 500) 
```

#### Lift

```{r}
plot_lift_curve(performance_dat_ppcr, interactive = params$interactive,
               size = 500)
```

#### Precision Recall

```{r}
plot_precision_recall_curve(performance_dat_ppcr, interactive = params$interactive,
               size = 500) 
```

#### Gains

```{r}
plot_gains_curve(performance_dat_ppcr, 
                 interactive = params$interactive,
               size = 500) 
```

# Utility (Decision Curve)

```{r}
plot_decision_curve(performance_dat, 
                    interactive = params$interactive, 
                    type = "combined",
                    size = 500) 
```

# Performance Table {.tabset}

## By Probability Threshold

```{r}
render_performance_table(performance_dat) 
```

## By Predicted Positives Condition Rate (PPCR)

```{r}
render_performance_table(performance_dat_ppcr)
```

```{css echo=FALSE}

.form-control {
  font-family: system-ui, sans-serif;
  font-size: 2rem;
  font-weight: bold;
  line-height: 1.1;
  display: grid;
  grid-template-columns: 1em auto;
  gap: 0.5em;
  place-content: center;
}

.form-control + .form-control {
  margin-top: 1em;
}

input[type="checkbox"] {
  -webkit-appearance: none;
  appearance: none;
  background-color: #fff;
  margin: 0;
  font: inherit;
  width: 1.15em;
  height: 1.15em;
  border: 0.15em solid currentColor;
  border-radius: 0.15em;
  transform: translateY(-0.075em);
  display: grid;
  place-content: center;
}


input[type="checkbox"][value="1"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #1b9e77;
  background-color: CanvasText;
}


input[type="checkbox"][value="2"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #d95f02;
  background-color: CanvasText;
}

input[type="checkbox"][value="3"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #7570b3;
  background-color: CanvasText;
}

input[type="checkbox"][value="4"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #e7298a;
  background-color: CanvasText;
}

input[type="checkbox"][value="5"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #07004D;
  background-color: CanvasText;
}

input[type="checkbox"][value="6"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #E6AB02;
  background-color: CanvasText;
}

input[type="checkbox"][value="7"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #FE5F55;
  background-color: CanvasText;
}

input[type="checkbox"][value="8"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #54494B;
  background-color: CanvasText;
}

input[type="checkbox"][value="9"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #006E90;
  background-color: CanvasText;
}

input[type="checkbox"][value="10"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #BC96E6;
  background-color: CanvasText;
}

input[type="checkbox"][value="11"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #52050A;
  background-color: CanvasText;
}

input[type="checkbox"][value="12"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #1F271B;
  background-color: CanvasText;
}

input[type="checkbox"][value="13"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #BE7C4D;
  background-color: CanvasText;
}

input[type="checkbox"][value="14"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #63768D;
  background-color: CanvasText;
}

input[type="checkbox"][value="15"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #08A045;
  background-color: CanvasText;
}

input[type="checkbox"][value="16"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #320A28;
  background-color: CanvasText;
}

input[type="checkbox"][value="17"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #82FF9E;
  background-color: CanvasText;
}

input[type="checkbox"][value="18"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #2176FF;
  background-color: CanvasText;
}

input[type="checkbox"][value="19"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #D1603D;
  background-color: CanvasText;
}

input[type="checkbox"][value="20"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #585123;
  background-color: CanvasText;
}

input[type="checkbox"]:checked::before {
  transform: scale(1);
}


```
