---
title: "Summary Report"
output: 
  html_document:
    toc: true
params:
  probs: NA
  reals: NA
  interactive: NA
---

<style type="text/css">
.main-container {
  max-width: 1040px;
  margin-left: auto;
  margin-right: auto;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(rtichoke)
library(dplyr)
```



<details>
  <summary>Performance Metrics Cheat Sheet</summary>
  
<br>  
    
```{r}
tibble::tribble(
  ~"type", ~"predicted_positive", ~"predicted_negative",
  "Real Positive", "TP", "FN",
  "Real Negative", "FP", "TN"
) %>% 
  reactable::reactable(sortable = FALSE,
            fullWidth = FALSE,
            borderless = FALSE,
            defaultColDef = reactable::colDef(
              align = "center",
              headerStyle  = list(fontWeight = 100)
            ),
            columns = list(
              type = reactable::colDef(
                name = "",
                align = "left",
                style = list(fontWeight = 100),
                minWidth = 110
              ),
              predicted_positive = reactable::colDef(
                name = "Predicted Positive",
                style = function(value) {
                  color <- if (value == "TP") {
                    "lightgreen"
                  } else if (value == "FP") {
                    "pink"
                  }
                  list(fontWeight = 600, background = color)
                }
            ),
            predicted_negative = reactable::colDef(
              name = "Predicted Negative",
              style = function(value) {
                color <- if (value == "TN") {
                  "lightgreen"
                } else if (value == "FN") {
                  "pink"
                }
                list(fontWeight = 600, background = color)
              }
            )
            )
  )
```

<br>
<br>
$\begin{aligned}
{\text{Prevalence}} = \frac{\text{TP + FN}}{\text{TP + FP + TN + FN}}
\end{aligned}$

<br>  

$\begin{aligned}
{\text{PPCR (Predicted Positives Condition Rate)}} = \frac{\text{TP + FP}}{\text{TP + FP + TN + FN}}
\end{aligned}$

<br>  

$\begin{aligned}
\text{Sensitivity (Recall, True Positive Rate)} = \frac{\text{TP}}{\text{TP + FN}} = \frac{\text{TP}}{\text{Real Positives}} = \text{Prob( Predicted Positive | Real Positive )}
\end{aligned}$

<br>  

$\begin{aligned}
\text{Specificity (True Negative Rate)} = \frac{\text{TN}}{\text{TN + FP}} = \frac{\text{TN}}{\text{Real Negatives}} = \text{Prob( Predicted Negative | Real Negative )}
\end{aligned}$

<br>  

$\begin{aligned}
    \text{PPV (Precision)} = \frac{\text{TP}}{\text{TP + FP}} = \frac{\text{TP}}{\text{Predicted Positives}} = \text{Prob( Real Positive | Predicted Positive )}
\end{aligned}$
  
<br>  

$\begin{aligned}
    \text{NPV} = \frac{\text{TN}}{\text{TN + FN}} = \frac{\text{TN}}{\text{Predicted Negatives}} = \text{Prob( Real Negative | Predicted Negative )}
\end{aligned}$
  
<br>  

$\begin{aligned}
\text{Lift} = \frac{\text{PPV}}{\text{Prevalence}} = \frac{\cfrac{\text{TP}}{\text{TP + FP}}}{\cfrac{\text{TP + FN}}{\text{TP + FP + TN + FN}}} 
\end{aligned}$
  
<br>  

$\begin{aligned}
\text{Net Benefit} = \frac{\text{TP}}{\text{TP + FP + TN + FN}} - \frac{\text{FP}}{\text{TP + FP + TN + FN}} * {\frac{{p_{t}}}{{1 - p_{t}}}}
\end{aligned}$
  
<br>  

</details>

<br>
<br>

```{r echo=FALSE}
# tibble(
#   "Model" = c("Test"),
#   "bs" = c(
#   sum((params$probs - params$reals)^2) / length(params$probs)#,
#   # sum((params$probs[[2]] - params$reals[[2]])^2) / length(params$probs[[1]])
#   ),
#   "auc" = c(
#   pROC::auc(params$reals, params$probs)),
#   # pROC::auc(params$reals[[2]], params$probs[[2]])),
#   "prevalence" = sum(params$reals) / length(params$reals)  #c(0.29, 0.41)
#   ) %>% 
#   mutate(
#     bs_plot = bs * 100,
#     bs_plot = purrr::map2(
#       bs_plot, bs, 
#       .f = ~rtichoke:::bar_chart(value = .x, display = .y, color = "pink", digits = 2))
#   ) %>% 
#   mutate(
#     auc_plot = auc * 100,
#     auc_plot = purrr::map2(
#       auc_plot, auc, 
#       .f = ~rtichoke:::bar_chart(value = .x, display = .y, color = "lightgreen", digits = 2))
#   ) %>% 
#   mutate(
#     prevalence_plot = prevalence * 100,
#     prevalence_plot = purrr::map2(
#       prevalence_plot, prevalence, 
#       .f = ~rtichoke:::bar_chart(value = .x, display = .y, color = "lightgrey", digits = 2))
#   ) %>% 
#   select(Model, bs_plot, auc_plot, prevalence_plot) %>% 
#   gt::gt() %>% 
#   gt::cols_align(
#     align = "left",
#     columns = gt::everything()
#   ) %>% 
#   gt::cols_width(
#     everything()~gt::px(100)
#   ) %>%
#   gt::cols_label(
#     bs_plot = "Brier Score",
#     auc_plot = "AUROC",
#     prevalence_plot = "Prevalence"
#   ) %>%
#   gt::tab_options(
#     table.align = "left",
#     # column_labels.hidden = TRUE,
#     table_body.border.bottom.color = "white",
#     table_body.border.top.color = "white",
#   )

```


```{r message=FALSE, warning=FALSE}
performance_dat <- prepare_performance_data(probs = params$probs, 
                         reals = params$reals)
```

```{r}
create_table_for_prevalence(performance_dat)
```



# Calibration {.tabset}

## Smooth

```{r message=FALSE, warning=FALSE}
create_calibration_curve(probs = params$probs, 
                         reals = params$reals, 
                         interactive = params$interactive, 
                         type = "smooth", size = 550) %>% 
  {if(params$interactive == TRUE) plotly::partial_bundle(.) else .}
```


<!-- ```{r} -->
<!-- create_table_for_brier_score(probs = params$probs,  -->
<!--                          reals = params$reals) -->
<!-- ``` -->


## Discrete

```{r message=FALSE, warning=FALSE}
create_calibration_curve(probs = params$probs, 
                         reals = params$reals, 
                         interactive = params$interactive, 
                         size = 550) %>% 
  {if(params$interactive == TRUE) plotly::partial_bundle(.) else .}
```



<!-- ```{r} -->
<!-- create_table_for_brier_score(probs = params$probs,  -->
<!--                          reals = params$reals) -->
<!-- ``` -->


# Probability Threshold Dependent Performance Metrics{.tabset}

```{r}
create_table_for_auc(probs = params$probs, 
                     reals = params$reals)
```


## By Probability Threshold

### Performance Metrics Curves {.tabset}

#### ROC


```{r}
plot_roc_curve(performance_dat, interactive = params$interactive, 
               size = 500) %>% 
  {if(params$interactive == TRUE) plotly::partial_bundle(.) else .}
  
```

#### Lift

```{r}
plot_lift_curve(performance_dat, interactive = params$interactive, 
                size = 500) %>% 
  {if(params$interactive == TRUE) plotly::partial_bundle(.) else .}
```


#### Precision Recall

```{r}
plot_precision_recall_curve(performance_dat, interactive = params$interactive,
                            size = 500) %>% 
  {if(params$interactive == TRUE) plotly::partial_bundle(.) else .}
```

#### Gains

```{r}
plot_gains_curve(performance_dat, interactive = params$interactive, 
                 size = 500) %>% 
  {if(params$interactive == TRUE) plotly::partial_bundle(.) else .}
```


#### Decision

```{r}
plot_decision_curve(performance_dat, interactive = params$interactive, 
                    size = 500) %>% 
  {if(params$interactive == TRUE) plotly::partial_bundle(.) else .}
```


### Performance Table

```{r}
render_performance_table(performance_dat) 
```

## By Predicted Positives Condition Rate (PPCR)

### Performance Metrics Curves {.tabset}

#### ROC

```{r message=FALSE, warning=FALSE}
performance_dat_ppcr <- prepare_performance_data(probs = params$probs, 
                         reals = params$reals, 
                         stratified_by = "ppcr")
```

```{r}
plot_roc_curve(performance_dat_ppcr, interactive = params$interactive,
               size = 500) %>% 
  {if(params$interactive == TRUE) plotly::partial_bundle(.) else .}
```

#### Lift

```{r}
plot_lift_curve(performance_dat_ppcr, interactive = params$interactive,
               size = 500) %>% 
  {if(params$interactive == TRUE) plotly::partial_bundle(.) else .}
```


#### Precision Recall

```{r}
plot_precision_recall_curve(performance_dat_ppcr, interactive = params$interactive,
               size = 500) %>% 
  {if(params$interactive == TRUE) plotly::partial_bundle(.) else .}
```

#### Gains

```{r}
plot_gains_curve(performance_dat_ppcr, interactive = params$interactive,
               size = 500) %>% 
  {if(params$interactive == TRUE) plotly::partial_bundle(.) else .}
```


#### Decision

```{r}
plot_decision_curve(performance_dat_ppcr, interactive = params$interactive,
               size = 500) %>% 
  {if(params$interactive == TRUE) plotly::partial_bundle(.) else .}
```


### Performance Table

```{r}
render_performance_table(performance_dat_ppcr)
```



```{css echo=FALSE}

.form-control {
  font-family: system-ui, sans-serif;
  font-size: 2rem;
  font-weight: bold;
  line-height: 1.1;
  display: grid;
  grid-template-columns: 1em auto;
  gap: 0.5em;
  place-content: center;
}

.form-control + .form-control {
  margin-top: 1em;
}

input[type="checkbox"] {
  -webkit-appearance: none;
  appearance: none;
  background-color: #fff;
  margin: 0;
  font: inherit;
  width: 1.15em;
  height: 1.15em;
  border: 0.15em solid currentColor;
  border-radius: 0.15em;
  transform: translateY(-0.075em);
  display: grid;
  place-content: center;
}


input[type="checkbox"][value="1"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #5BC0BE;
  background-color: CanvasText;
}


input[type="checkbox"][value="2"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #FC8D62;
  background-color: CanvasText;
}

input[type="checkbox"][value="3"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #8DA0CB;
  background-color: CanvasText;
}

input[type="checkbox"][value="4"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #E78AC3;
  background-color: CanvasText;
}

input[type="checkbox"][value="5"]::before {
  content: "";
  width: 0.65em;
  height: 0.65em;
  transform: scale(0);
  box-shadow: inset 1em 1em #A4243B;
  background-color: CanvasText;
}

input[type="checkbox"]:checked::before {
  transform: scale(1);
}


```